### 2007-10-30 pkg/paper/Colorspace/article.Rnw
added an idea for an example/demo to the colorspace article
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@15 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

>>>>

\section{An example}

As an example to demonstrate what all of this gives you, implement
a function that generates colours within a CIEHCL space where the
colours are as far apart from each other as possible, but limited
to a narrow L range and a narrow C range.  (The idea is to have
colours that differ mostly only in hue, but which still are 
distinguishable when printed in black-and-white.)  Then convert the
colours to RGB for sending to a screen device.
